---
title: "newtt17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(schrute)
library(tidytext)
library(tidylog)
library(ggridges)
library(viridis)
```

## Wrangle

```{r}
officedata <- schrute::theoffice
#read in data
male_mainchar<-c("Michael","Ryan","Jim","Andy", "Oscar", "Toby", "Stanley", "Dwight", "Kevin", "Darryl")
#variable contains list of the ten main characters that are male
female_mainchar<-c("Kelly", "Jan", "Pam", "Erin", "Oscar", "Angela", "Phyllis")
#variable contains list of the seven main characters that are female
officedata%>%
  unnest_tokens(word, text)%>%
  #reformat data such that each row contains only one token (word)
  mutate(gender = case_when(str_detect(character, paste(male_mainchar, collapse = "|"))~"male", 
                            str_detect(character, paste(female_mainchar, collapse = "|"))~"female"))%>%
  #create new variable with value "male" if any male main character is detected in the observation and value "female" if any female main character is detected in the observation
  count(season, episode, gender)%>%
  #get table counts
  pivot_wider(names_from = gender, values_from = n)%>%
  #create columns male and female
  mutate(wpmchar_f = female*(1/length(female_mainchar)),
           #create variable words per main character female
           wpmchar_m = male*(1/length(male_mainchar)),
           #create variable words per main character male
           ratio = wpmchar_f/wpmchar_m,
           #create variable ratio of female to male words per main character
           season_display = substr(season, start = 2, stop = 2))->wrangled2 #extract second value from season strings for display-ready format
wrangled2
```
## Plot
```{r, fig.height = 4, fig.width = 6}
  ggplot(wrangled2, aes(x = ratio, y = season_display, fill = stat(x)))+
    geom_density_ridges_gradient()+
    theme_minimal()+
    labs(title = "Gender Inequity in The Office (US)", 
           subtitle = "female to male words per main character by season", 
           caption = "Data from Schrute", 
           y="Season", 
           x= "F:M Ratio (words/main character)")+
  theme(text = element_text(size=14))+
  scale_fill_viridis(option = "viridis", name = "F:M Ratio")->textplot2
  textplot2
  ggsave(filename = "gender_equity2.png", plot = textplot2)
  
```
In creating this #tidytuesday submission, I learned that there are frequently multiple ways to accomplish the same goal when wrangling data. For instance, I initially used the function table() to count the instances of the values of gender in each season, and the function as_tibble() to convert that output back into a tibble. However, as Dr. Spielman pointed out, I could just as easily have used the construction count(gender, season). Later, when I realized I wanted to create a ridge plot rather than a line plot, I used the count() function to count combinations of episode, season and gender. According to the documentation for this function, count() is equivalent to calling group_by(), tally(), and ungroup(); it also has the advantage of speed over table() if one is summarizing multiple variables because it does not record combinations which occur 0 times. 

