---
title: "US College Tuition"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggforce)
library(RColorBrewer)
```

## Tidy Tuesday 3/10/2020


```{r}
tuition_cost <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-10/tuition_cost.csv') #read in dataset
```

## Plot

```{r, fig.height=4, fig.width=6}

tuition_cost%>%
  filter(type %in% c("Private", "Public", "For Profit"))%>% #remove observations with type other than Private, Public, or For Profit
  ggplot(aes(y=in_state_tuition, x=type))+
  geom_sina(aes(color=type))+
  scale_color_brewer(palette = "Dark2", name="School Type")+ 
  theme_minimal()+
  labs(title = "In-State Tuition of US Colleges", subtitle = "2018-2019 School Year", caption = "Data from The Chronicle of Higher Education", y="In-State Tuition (USD)", x= "School Type")+
  theme(axis.title.x = element_blank(), text = element_text(size=14))->march10tt

march10tt

ggsave("march10tt.png", plot = march10tt)
```

While making this tidy tuesday submission I was reminded that one should always be sure they are using the appropriate package for some task (in this case I had initially downloaded the package sinaplot by mistake, which requires plyr and is not tied to ggplot2). I also learned how to omit the axis title from a ggplot using the element_blank() function, and tried to apply certain lessons from Claus Wilke's data viz book (for example, by increasing the text size).
